\Sof{TBA - New Titles in the comments}

### 2020-05-08 paper/icsme20.tex
polishing motivation

As an example, consider the patch of the Online Certificate Status Procotol (OCSP) 
implementation in OpenSSL\footnoteref{openssl} to address a memory leak flaw 
found in the way OpenSSL handled TLS status request extension data during session 
renegotiation and where a remote attacker could cause a Denial-of-Service
(DoS) attack - through memory consumption - via large OCSP Status Request extensions.
OCSP, formally known as the TLS Certificate Status Request extension, is a protocol 
that allows the client to verify the server certificate for revocation.

@@

Every SSL/TLS connection begins with a handshake 
which is responsible for the negotiation between the two parties. 
The OSCP Status Request extension allows the client to verify
the server certificate and enables a TLS server to include
its response in the handshake. The problem in CVE-$2016$-$6304$
is that if the client systematically requests a renegotiation,
while sending large OCSP Status Request extensions each time,
then there will be unbounded memory growth on the server
and lead to a Denial-of-Service attack through memory exhaustion. 
Applications not enabling OCSP stapling support are not affected.

>>>>

As an example, consider the patch of the TLS state machine protocol implementation
in OpenSSL\footnoteref{openssl} to address a memory leak flaw 
found in the way OpenSSL handled TLS status request extension data during session 
renegotiation and where a malicious client could cause a Denial-of-Service
(DoS) attack via large OCSP Status Request extensions - if OCSP stapling support
enabled. Online Certificate Status Procotol (OCSP) stapling, formally known as the TLS Certificate 
Status Request extension, is a standard for checking the revocation status of
certificates.

@@

Every SSL/TLS connection begins with a handshake 
which is responsible for the negotiation between the two parties. 
The OSCP Status Request extension allows the client to verify
the server certificate and enables a TLS server to include
its response in the handshake. The problem in CVE-$2016$-$6304$
was a flaw in the logic of OpenSSL, a client 
can systematically requests renegotiation,
while sending large OCSP Status Request extensions each time. This
increases the amount of unbounded memory on the server
which will eventually lead to a DoS attack through memory exhaustion. 
Applications not enabling OCSP stapling support are not affected.
